---
title: "COCOA & CHOCOLATE"
author: "Tan Su Rong (P120754)"
output: 
  flexdashboard::flex_dashboard: 
   storyboard: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE)
library(ggplot2)
library(gganimate)
library(tidyr)
library(dplyr)
library(stringr)
library(plotly)
library(tidytext)
library(wordcloud2)
```

General {.storyboard}
======================================

### About Cocoa Beans


The beans which have been derived from the Cocoa tree are called Cocoa beans. 

The other common names for Cocoa bean are Cocoa, Cacao and Cacao bean.

It is the key ingredients of making chocolate.

Cocoa is loaded with antioxidants to provide anti-aging properties and high concentration of Epicatechin that is helpful for cardiovascular health. 

Largest exporters of Cocoa beans: Ghana, Cote d’Ivoire, Ecuador, Nigeria and Cameroon

Main importers of Cocoa beans: United States, Netherlands, Belgium-Luxembourg and Malaysia

Reference link: https://www.healthbenefitstimes.com/cocoa-bean/

General:

The storyboard is about the trend of cocoa production in worldwide, 
the nutrition facts of chocolate types and products with chocolate. 

The next visualizations are about chocolate bars in the world. 
The content is related to the number of ingredients, cocoa percentage, 
ratings and characteristics of chocolate bars.

Malaysia:

The frames are about export, import and the production of cocoa beans.



### World Production of Cocoa Beans

```{r include=FALSE}
world_prod <- read.csv("cocoa.csv")

world_prod_plot <- 
  ggplot(data = world_prod, aes(x = Year, y = Total)) +
  geom_line(colour = "chocolate", size = 1) +
  geom_point(colour = "chocolate", shape = 3, size = 5) +
  geom_text(aes(label = Total), vjust = -1, size = 7,
            colour = "chocolate1", fontface = "bold") +
  labs(y = "Production (tons)",
       title = "Worldwide Cocoa Production from 1961 to 2021") +
  transition_reveal(Year) +
  theme(plot.title = element_text(face = "bold", colour = "chocolate4", size = 25),
        axis.text = element_text(face = "bold", size = 18),
        axis.title = element_text(face = "bold", colour = "chocolate4", size = 20),
        panel.grid.major = element_line(colour = "bisque"),
        panel.grid.minor = element_line(colour = "bisque"),
        panel.background = element_rect(fill = "lightyellow"))

world_prod_plot <- animate(world_prod_plot, width = 1000, height = 800)
```
```{r}
world_prod_plot
```

> 
> Source of data: Food and Agriculture Organization of the United Nations, Retrieved from: https://www.fao.org/faostat/en/#data/QCL

***
- The worldwide production of cocoa beans were recorded from 1961 to 2021. 
The data collected consist of Official figure, Unofficial figure, 
Estimated value, Imputed value and even Missing value due to data cannot exist or not applicable.

- The line of total production shows fluctuation throughout the years 
but the trend shows an increasing pattern.



### Nutrition Facts of Chcocolate Types

```{r include=FALSE}
nutrient <- read.csv("nutrients.csv")
nutrient <- pivot_longer(nutrient, 
                         cols = c("Black_40", "Black_70", 
                                  "Milk_Choco", "White_Choco"),
                         names_to = "Chocolate_Type", values_to = "Value")
nutrient <- as.data.frame(nutrient)
nl <- as.list(unique(nutrient$Nutrients))
```

```{r}
selectInput("select_nl", label = "Select Nutrients:",
            choices = nl, selected = "Energy(kcal)")
```

```{r}
renderPlot({
  n <- nutrient[nutrient$Nutrients == input$select_nl,]
  ggplot(data = n, aes(x = Chocolate_Type, y = Value)) +
  geom_bar(stat = "identity", fill = "burlywood") +
  labs(x = "Type of Chocolate", y = input$select_nl,
       title = paste("Value of", input$select_nl, "in 100g of Each Chocolate Type")) +
  scale_x_discrete(labels = c("Dark Chocolate \n40% Cocoa", 
                              "Dark Chocolate \n70% Cocoa", 
                              "Milk Chocolate", "White Chocolate")) +
  geom_text(aes(label = round(Value, 2)), 
            vjust = -0.5, colour = "chocolate",
            fontface = "bold", size = 7) +
  theme(plot.title = element_text(face = "bold", colour = "chocolate4", size = 22),
       # plot.margin = margin(0, 30, 5, 2, "cm"), #(top, right, bottom, left, "unit")
        axis.text = element_text(face = "bold", size = 16),
        axis.title = element_text(face = "bold", colour = "chocolate4", size = 18),
        panel.grid.major = element_line(colour = "bisque"),
        panel.grid.minor = element_line(colour = "bisque"),
        panel.background = element_rect(fill = "lightyellow"))
}, width = 900, height = 650)
```

> 
> Source of data: Chocolate Advisor, Retrieved from: https://www.chocolate-advisor.com/guides/chocolate-nutrition-facts

***
- The common types of chocolate in the market are Dark Chocolate with 40% of Cocoa, 
Dark Chocolate with 70% of Cocoa, Milk Chocolate and White Chocolate. 
Their nutritional values are always being compared by people.

- The bar chart illustrates the values of nutritional value for each chocolate type.

- Example: In 100g of Dark Chocolate with 40% of Cocoa, 
there is only 498kcal of Energy which is the lowest among the four.



### Nutrition Facts of Product with Chocolate

```{r include=FALSE}
product <- read.csv("choc_products.csv")
product <- pivot_longer(product, cols = c("Fat_g", "Carbs_g", "Protein_g"),
                        names_to = "Nutrients", values_to = "Value")
product <- as.data.frame(product)
pl <- as.list(unique(product$Product))
```

```{r}
selectInput("select_pl", label = "Select a product:",
            choices = pl, selected = "Cornmeal Beverage With Chocolate Milk")
```

```{r}
renderPlot({
  p <- product[product$Product == input$select_pl,]
  ggplot(data = p, aes(x = Nutrients, y = Value)) +
  geom_bar(stat = "identity", fill = "burlywood") +
  labs(x = "Nutrients of Products with Chocolate", 
       y = "Nutritional Value (g)",
       title = paste("Carbs, Fats and Proteins in \n100g of", input$select_pl)) +
  geom_text(aes(label = round(Value, 2)), 
            vjust = -0.3, colour = "chocolate1",
            fontface = "bold", size = 6) +
  theme(plot.title = element_text(face = "bold", colour = "chocolate4", size = 20),
      #  plot.margin = margin(0, 30, 5, 2, "cm"), #(top, right, bottom, left, "unit")
        axis.text = element_text(face = "bold", size = 14),
        axis.title = element_text(face = "bold", colour = "chocolate4", size = 16),
        panel.grid.major = element_line(colour = "bisque"),
        panel.grid.minor = element_line(colour = "bisque"),
        panel.background = element_rect(fill = "lightyellow"))
}, width = 900, height = 650)
```

> 
> Source of data: Selina Wamucii , Retrieved from: https://www.selinawamucii.com/nutrition/?s=chocolate&post_type=product, 21 pages As of 11 July 2023

***
- Chocolate is widely added into food products in the market. 

- The figure displays the value of Carbohydrates, Fat and Protein in the selected product.

- Example: There are 20.98g of carbs, 2.38g of fat and 1.89g of protein in a 
100g of Cornmeal Beverage With Chocolate Milk.


### Number of Ingredients in Chocolate Bar

```{r include=FALSE}
chocolate <- read.csv("choco_bar.csv")
ing_no <- subset(chocolate, select = "Ingredients")

ing_no <- na.omit(ing_no)
ing_no <- as.data.frame(ing_no %>% group_by(Ingredients) %>%
                          summarise(Total = n()))

ing_no_plot <-
  ggplot(data = ing_no, aes(x = as.factor(Ingredients), y = Total)) +
  geom_bar(stat = "identity", fill = "burlywood") +
  labs(x = "Number of Ingredients in the Chocolate Bar", 
       y = "Number of Chocolate Bar",
       title = "Total Number of Chocolate Bars") +
  geom_text(aes(label = Total), 
            vjust = -0.3, colour = "chocolate1",
            fontface = "bold", size = 6) +
  theme(plot.title = element_text(face = "bold", colour = "chocolate4", size = 24),
        axis.text = element_text(face = "bold", size = 16),
        axis.title = element_text(face = "bold", colour = "chocolate4", size = 20),
        panel.grid.major = element_line(colour = "bisque"),
        panel.grid.minor = element_line(colour = "bisque"),
        panel.background = element_rect(fill = "lightyellow"))
```

```{r}
renderPlot({ing_no_plot}, width = 1000, height = 700)
```

> 
> Source of data: Flavors of Cacao, Retrieved from: http://flavorsofcacao.com/chocolate_database.html, Updated on: June 17, 2023

***
- The main ingredients in a chocolate bar, except the Beans, could be Sugar, 
Sweetener other than white cane or beet sugar, Cocoa Butter, Vanilla, Lecithin and Salt.

- There are 1 to 6 types of ingredients combined to make a chocolate bar.

- Among 2,570 types of chocolate bars, 1109 are made of 3 basic ingredients. 
The combination may be Beans, Sugar or Sweetener and Cocoa Butter or others. 


### Number of Ingredients and Cocoa Percentage in Chocolate Bar

```{r include=FALSE}
chocolate <- read.csv("choco_bar.csv")
ing_pct <- subset(chocolate, select = c("Cocoa.Percent", "Ingredients"))
ing_pct <- na.omit(ing_pct)
ing_pct$Cocoa.Percent <- str_remove_all(ing_pct$Cocoa.Percent, "%")
ing_pct$Cocoa.Percent <- round(as.numeric(ing_pct$Cocoa.Percent), 2)
ing_pct <- as.data.frame(ing_pct %>% 
                        group_by(Ingredients, Cocoa.Percent) %>% 
                        summarise(Count = n()))
ipl <- as.list(unique(ing_pct$Ingredients))
```

```{r}
selectInput("select_ipl", label = "Number of Ingredients:",
            choices = ipl, selected = 4)
```

```{r}
renderPlotly({
  ni <- ing_pct[ing_pct$Ingredients == input$select_ipl,]
  # axes
  f1 <- list(size = 18, color = "chocolate")
  f2 <- list(size = 16, color = "black")
  x <- list(title = "Percentage of Cocoa", titlefont = f1, tickfont = f2)
  y <- list(title = "Number of Chocolate Bar", titlefont = f1, tickfont = f2)

  # title
  f3 <- list(size = 20, color = "chocolate4")
  t <- list(text = paste("Chocolate Bars with", input$select_ipl, "Ingredients"),
          font = f3)

  # hover
  h <- list(bgcolor = "lightyellow", bordercolor = "chocolate",
          font = list(color="black"))
  
  plot_ni <- 
  plot_ly(data = ni, x = ~as.factor(Cocoa.Percent), y = ~Count,
          hovertemplate = ~paste("Cocoa:", Cocoa.Percent, "%",
                                 "<br>Count:", Count, "<extra></extra>"),
          width = 1200, height = 650) %>%
  add_bars(color = I("burlywood"), name = "") %>%
  layout(title = t, xaxis = x, yaxis = y, hoverlabel = h,
         margin = list(l = 50,r = 10, b = 10, t = 50, pad =2))

  plot_ni
})
```

> 
> Source of data: Flavors of Cacao, Retrieved from: http://flavorsofcacao.com/chocolate_database.html, Updated on: June 17, 2023


***
- Different percentage of cocoa can be found in chocolate bars.

- The figure reveals the number of chocolate bars for various cocoa percentage 
with specific number of ingredients.

- Example: Most chocolate bars with 4 ingredients are with 70% of cocoa.

### Ingredients, Cocoa Percentage & Ratings

```{r include=FALSE}
chocolate <- read.csv("choco_bar.csv")

rate <- subset(chocolate, select = c("Ingredients", "Cocoa.Percent", "Rating"))
rate <- na.omit(rate)
rate$Cocoa.Percent <- str_remove_all(rate$Cocoa.Percent, "%")
rate$Cocoa.Percent <- round(as.numeric(rate$Cocoa.Percent), 2)
```

```{r}
renderPlotly({
  # axes
  f1 <- list(size = 18, color = "chocolate")
  f2 <- list(size = 16, color = "black")
  x <- list(title = "Ratings of Chocolate Bar", titlefont = f1, tickfont = f2)
  y <- list(title = "Percentage of Cocoa", titlefont = f1, tickfont = f2)

  # title
  f3 <- list(size = 20, color = "chocolate4")
  t <- list(text = "Cocoa Percentage and Ratings of Chocolate Bar",
            font = f3)

  # legends
  l <- list(font = list(size = 12), #orientation = "h",
            title = list(text='<b> Number of Ingredients: </b>'))

  # hover
  h <- list(bgcolor = "lightyellow", bordercolor = "chocolate",
            font = list(color="black"))

  mycol <- c("red", "orange", "gold", "green", "dodgerblue", "darkorchid")

  plot_ly(data = rate, x = ~as.numeric(Rating), y = ~as.numeric(Cocoa.Percent),
          text = ~paste("Cocoa:", Cocoa.Percent, "%",
                        "<br>Rating:", Rating,
                        "<br>Number of Ingredients:", Ingredients),
          mode = "markers", hoverinfo = "text", 
          width = 1500, height = 700) %>%
  add_markers(color = ~as.factor(Ingredients), alpha = 0.4,
              colors = mycol) %>%
  layout(title = t,
         xaxis = x, yaxis = y,
         legend = l, hoverlabel = h,
         margin = list(l = 50,r = 10, b = 10, t = 50, pad =2))
})
```

> 
> Source of data: Flavors of Cacao, Retrieved from: http://flavorsofcacao.com/chocolate_database.html, Updated on: June 17, 2023

***
- The colour of a point is determined by the number of ingredients in the chocolate bar.
Each point, representing one type of chocolate bar, will show the percentage of cocoa, 
the ratings and the number of ingredients when hover.

- The distribution is denser at the range from 60% to 85% of cocoa percentage with the ratings 
ranged from 2.00 to 4.00 despite the number of ingredients in the chocolate bars.

- To check on the cocoa percentage together with the ratings for a specific of number of ingredients, 
click at the legend to hide the undesired number and get a clearer view.

- Example: With 1 ingredient which is definitely cocoa only, the percentage is 100% for all chocolate bars. 
The ratings for these dark chocolates are 2.50, 2.75, 3.00 and 3.50 as shown in the plot.


### Characteristics by Country of Origin

```{r include=FALSE}
# Load data
chocolate <- read.csv("choco_bar.csv")

# Select columns
c_choco <- chocolate[, c("Origin", "Characteristics")]

# Split the Characteristics into individual words
c_choco <- unnest_tokens(c_choco, word, Characteristics)

# Remove the word "cocoa" and stop words
c_choco <- c_choco[!c_choco$word == "cocoa",]
c_choco <- c_choco %>% anti_join(stop_words)

# colour palette
pal <- colorRampPalette(c("#3F2305", "#FFF8D5"))(30)

origin <- as.list(unique(c_choco$Origin))
```

```{r}
selectInput("origin", label = "Select the Origin of Cocoa Beans:",
            choices = origin, selected = "Colombia")
```

```{r}
renderWordcloud2({
  c_origin <- c_choco[c_choco$Origin == input$origin,]
  c_data <- c_origin %>% count(word, sort = TRUE)
  wordcloud2(data = c_data, size = 0.8, color = pal, shuffle = F,
           rotateRatio = 0, shape = "rectangle")
})

```


> 
> Source of data: Flavors of Cacao, Retrieved from: http://flavorsofcacao.com/chocolate_database.html, Updated on: June 17, 2023

***
- The words shown in the figure is the most memorable characteristics of 
chocolate bars made from the cocoa beans from the selected country of origin. 
Terms generally relate to anything from texture, flavor, overall opinion, etc.

- Darker font color and bigger font size indicates the word is highly used to
describe the bars as compared to others.

- Example: For chocolate bars made from the cocoa beans from Colombia, 
the most frequent words used to describe the characteristics are 
"marshmallow" (16 times), "nutty" (16 times), "sweet" (13 times) and "fruit" (9 times).


Malaysia {.storyboard}
====================================== 
 
### Export of Cocoa Beans by Malaysia

```{r include=FALSE}
export <- read.csv("export_beans.csv")

```

```{r}
renderPlotly({
  # axes
  f1 <- list(size = 18)
  f2 <- list(size = 16)
  x <- list(title = "Year", titlefont = f1, tickfont = f2)
  y <- list(titlefont = f1, tickfont = f2)

  # title
  f3 <- list(size = 20)
  t <- list(text = "Export Amount of Cocoa Beans by Quantity, Value & FOB",
            font = f3)

  # legends
  l <- list(x = 0.85, font = list(size = 12),
            title = list(text='<b> Export: </b>'))

  # hover
  h <- list(bgcolor = "lightyellow", bordercolor = "chocolate",
            font = list(color="black"))
  
  subplot(
  plot_ly(export, x = ~Year, y = ~Quantity,
          text = ~paste("Year: ", Year,
                        "<br>Export Quantity:", Quantity, "Tonne"),
          hoverinfo = "text", height = 700) %>% 
    add_lines(name="Quantity (Tonne)") %>%
    layout(yaxis = y),
  plot_ly(export, x = ~Year, y = ~Value,
          text = ~paste("Year: ", Year,
                        "<br>Export Value: RM", Value, "k"),
          hoverinfo = "text", height = 700) %>% 
    add_lines(name="Value (RM'000)") %>%
    layout(yaxis = y),
  plot_ly(export, x = ~Year, y = ~FOB,
          text = ~paste("Year: ", Year,
                        "<br>Export FOB: RM", FOB, "/Tonne"),
          hoverinfo = "text", height = 700) %>% 
    add_lines(name="FOB (RM/Tonne)") %>%
    layout(yaxis = y),
  nrows = 3, shareX = TRUE, widths = 0.6) |>
  layout(title = t, xaxis = x, legend = l,
         hoverlabel = h, hovermode = "x unified",
         margin = list(l = 10, r = 10, b = 50, t = 80, pad = 2))
})
```

> 
> Source of data: Department of Statistics Malaysia, Retrieved from: https://www.koko.gov.my/lkm/industry/statistic/export.cfm

***
- The plots show the export of cocoa beans by Malaysia in terms of quantity, 
monetary value and Free on Board (FOB).

- With constant quantity, FOB increases as the monetary value increases.
With static monetary value, FOB decreases as the quantity increases.

- The data collected is from 1992 until 2022. 
The exports decreased since 1992 but increased from 2010 to 2022 due to re-export.

- Malaysia hit the highest quantity and value of exports in 2018 with 
155,572 tonne of cocoa beans at RM 1,426,805,000. 

- The highest FOB recorded was RM 12,594/tonne in 2016.


### Import of Cocoa Beans by Malaysia

```{r include=FALSE}
import <- read.csv("import_beans.csv")

```

```{r}
renderPlotly({
  
  # axes
  f1 <- list(size = 18)
  f2 <- list(size = 16)
  x <- list(title = "Year", titlefont = f1, tickfont = f2)
  y <- list(titlefont = f1, tickfont = f2)

  # title
  f3 <- list(size = 20)
  t <- list(text = "Import Amount of Cocoa Beans by Quantity, Value & CIF",
            font = f3)

  # legends
  l <- list(x = 0.85, font = list(size = 12),
            title = list(text='<b> Import: </b>'))

  # hover
  h <- list(bgcolor = "lightyellow", bordercolor = "chocolate",
            font = list(color="black"))

  subplot(
  plot_ly(import, x = ~Year, y = ~Quantity,
          text = ~paste("Year: ", Year,
                        "<br>Import Quantity:", Quantity, "Tonne"),
          hoverinfo = "text", height = 700) %>% 
    add_lines(name="Quantity (Tonne)") %>%
    layout(yaxis = y),
  plot_ly(import, x = ~Year, y = ~Value,
          text = ~paste("Year: ", Year,
                        "<br>Import Value: RM", Value, "k"),
          hoverinfo = "text", height = 700) %>% 
    add_lines(name="Value (RM'000)") %>%
    layout(yaxis = y),
  plot_ly(import, x = ~Year, y = ~CIF,
          text = ~paste("Year: ", Year,
                        "<br>Import CIF: RM", CIF, "/Tonne"),
          hoverinfo = "text", height = 700) %>% 
    add_lines(name="CIF (RM/Tonne)") %>%
    layout(yaxis = y),
  nrows = 3, shareX = TRUE, widths = 0.6) |>
  layout(title = t, xaxis = x, legend = l,
         hoverlabel = h, hovermode = "x unified",
         margin = list(l = 10, r = 10, b = 50, t = 80, pad = 2))
})
```

> 
> Source of data: Department of Statistics Malaysia, Retrieved from: https://www.koko.gov.my/lkm/industry/statistic/import.cfm

***
- The plots show the import of cocoa beans by Malaysia in terms of quantity, 
monetary value and Cost, Insurance and Freight (CIF).

- With constant quantity, CIF increases as the monetary value increases.
With static monetary value, CIF decreases as the quantity increases.

- The graph shows the import index from 1992 to 2022. 
The imports increased since 1992, a sudden drop in 2009 and started to rise again after 2016.

- Highest quantity at 523,926 tonne of cocoa beans were imported by Malaysia in 2008 
and reached the highest import value of RM 5,010,786,000 in 2021

- The highest CIF recorded was RM 12,688/tonne in 2016.



### Production (Tonne) Of Cocoa Beans By Region in Malaysia

```{r include=FALSE}
region <- read.csv("region_data.csv")
region <- region %>% 
  pivot_longer(cols = c("West_Msia", "Sabah", "Sarawak", "Total"),
               names_to = "Region", values_to = "Production")
region <- as.data.frame(region)
region <- region %>% 
  mutate(Region = factor(Region, levels = c("West_Msia", "Sabah", "Sarawak", "Total")))

reg_col <- c("#eda268", "#8f3e00", "#583101", "#9ba2ff")

p <-
  ggplot(region, aes(x = Year, y = Production, colour = Region)) + 
  geom_line(size = 1) +
  scale_colour_manual(values = reg_col) +
  labs(x = "Year", y = "Production (Tonne)",
       title = "Production of Cocoa Beans in Malaysia",
       colour = "Region") +
  theme(plot.title = element_text(face = "bold", colour = "chocolate4", size = 22),
        plot.margin = margin(2, 1, 2, 1, "cm"), #(top, right, bottom, left, "unit")
        axis.text.x = element_text(face = "bold", size = 12),
        axis.text.y = element_text(face = "bold", size = 16),
        axis.title = element_text(face = "bold", colour = "chocolate4", size = 18),
        legend.title = element_text(face = "bold", colour = "chocolate4", size = 12),
        legend.text = element_text(size = 12),
        panel.grid.major = element_line(colour = "bisque"),
        panel.grid.minor = element_line(colour = "bisque"),
        panel.background = element_rect(fill = "white"))
```

```{r}
renderPlotly({
  ggplotly(p, tooltip = "all", dynamicTicks = TRUE, width = 1000) %>%
    layout(hovermode = "x unified")
})
```

> 
> Source of data: Department of Statistic Malaysia, Malaysia Cocoa Board, Retrieved from: https://www.koko.gov.my/lkm/industry/statistic/p_cocoabean.cfm

***
- The statistics of regional production of cocoa beans are shown in the figure. 
The production value in 2022 is the estimated value.

- The production increased from 1980 and reached its highest point 
at the total production of 80,800 tonne in 1990.
The amount dropped since then and currently getting lower which was not more than 500 tonne in 2022.

- Sabah contributed the most in the total production as compared to West Malaysia and Sarawak.

### Conclusion

- The increase in worldwide production of cocoa beans allows 
more type of chocolate bars and products to be introduced to the market.

- In general, people still prefer the percentage of cocoa between 60% to 85% 
and chocolate bars with two or three main ingredients. 
Not too pure for bitterness but not too sweet as well.

- Due to the decrease in cocoa plantation, the import is always higher than the export in Malaysia.

- This situation indicates that Malaysia is spending more for imports of cocoa beans than the gains from exports.
